Scheduling and Amortization for MPC

### 2022-02-11 biometric_vectorization_example.tex
Minor edit to Biometric code in Basic vectorization example.

{\small
\begin{verbatim}
min_sum!1 = 10000
min_index!1 = 0
for i in range(0, N!0):
   min_sum!2 = PHI(min_sum!1, min_sum!4)
   min_index!2 = PHI(min_index!1, min_index!4)
   sum!2 = 0
   for j in range(0, D!0):
     sum!3 = PHI(sum!2, sum!4)
     d!3 = (S!0[((i * D!0) + j)] - C!0[j])
     p!3 = (d!3 * d!3)
     sum!4 = (sum!3 + p!3)
   !1!2 = (sum!3 < min_sum!2)
   min_sum!3 = sum!3
   min_index!3 = i
   min_sum!4 = MUX(!1!2, min_sum!3, min_sum!2)
   min_index!4 = MUX(!1!2, min_index!3, min_index!2)
\end{verbatim}
}

@@

{\small
\begin{verbatim}
min_sum!1 = 10000
min_sum!1^ = raise_dim(min_sum!1, (i:N!0))
min_index!1 = 0
min_index!1^ = raise_dim(min_index!1, (i:N!0))
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0,j:D!0))
for i in range(0, N!0):
   min_sum!2 = PHI(min_sum!1^, min_sum!4)
   min_index!2 = PHI(min_index!1^, min_index!4) 
   sum!2 = 0 // Will lift, when hoisted
   sum!2^ = raise_dim(sum!2, (j:D!0)) // Special form?
   for j in range(0, D!0):
      sum!3 = PHI(sum!2^, sum!4)
      d!3 = S!0^ - C!0^
      p!3 = (d!3 * d!3) 
      sum!4 = (sum!3 + p!3)
   sum!3^ = drop_dim(sum!3)     
   !1!2 = (sum!3^ < min_sum!2)
   min_sum!3 = sum!3^
   min_index!3 = i  // Same-level, will lift when hoisted
   min_sum!4 = MUX(!1!2, min_sum!3, min_sum!2)
   min_index!4 = MUX(!1!2, min_index!3, min_index!2)
\end{verbatim}
}

@@

{\small
\begin{verbatim}
min_sum!1 = 10000
min_sum!1^ = raise_dim(min_sum!1, (i:N!0))
min_index!1 = 0
min_index!1^ = raise_dim(min_index!1, (i:N!0))
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0,j:D!0))
for i in range(0, N!0):
  min_sum!2[I] = PHI(min_sum!1^[I], min_sum!4[I]) 
  min_index!2[I] = PHI(min_index!1^[I], min_index!4[I])  
  sum!2 = [0,..,0] 
  sum!2^ = raise_dim(sum!2, (j:D!0))
  d!3[I,J] = S!0^[I,J] - C!0^[I,J]
  p!3[I,J] = (d!3[I,J] * d!3[I,J])
  for j in range(0, D!0):
    sum!3[I,j] = PHI(sum!2^[I,j], sum!4[I,j-1])       
    sum!4[I,j] = (sum!3[I,j] + p!3[I,j])
  sum!3^ = drop_dim(sum!3)     
  !1!2[I] = (sum!3^[I] < min_sum!2[I])
  min_sum!3 = sum!3^
  min_index!3 = [0,1,2,...,N!0-1]
  min_sum!4[I] = MUX(!1!2[I], min_sum!3[I], min_sum!2[I])
   min_index!4[I] = MUX(!1!2[I], min_index!3[I], min_index!2[I])
\end{verbatim}
}

@@

for i in range(0, N!0):
  min_index!2[i] = PHI(min_index!1^[i], min_index!4[i-1])  
   min_index!4[i] = MUX(!1!2[i], min_index!3[i], min_index!2[i])
\end{verbatim}
}

>>>>

{\small
\begin{verbatim}
min_sum!1 = 10000
min_index!1 = 0
for i in range(0, N!0):
   min_sum!2 = PHI(min_sum!1, min_sum!4)
   min_index!2 = PHI(min_index!1, min_index!4)
   sum!2 = 0
   for j in range(0, D!0):
     sum!3 = PHI(sum!2, sum!4)
     d!3 = (S!0[((i * D!0) + j)] - C!0[j])
     p!3 = (d!3 * d!3)
     sum!4 = (sum!3 + p!3)
   !1!2 = (sum!3 < min_sum!2)
   min_sum!3 = sum!3
   min_index!3 = i
   min_sum!4 = MUX(!1!2, min_sum!3, min_sum!2)
   min_index!4 = MUX(!1!2, min_index!3, min_index!2)
!2!1 = (min_sum!2, min_index!2)   
\end{verbatim}
}

@@

{\small
\begin{verbatim}
min_sum!1 = 10000
min_sum!1^ = raise_dim(min_sum!1, (i:N!0))
min_index!1 = 0
min_index!1^ = raise_dim(min_index!1, (i:N!0))
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0,j:D!0))
for i in range(0, N!0):
   min_sum!2 = PHI(min_sum!1^, min_sum!4)
   min_index!2 = PHI(min_index!1^, min_index!4) 
   sum!2 = 0 // Will lift, when hoisted
   sum!2^ = raise_dim(sum!2, (j:D!0)) // Special form?
   for j in range(0, D!0):
      sum!3 = PHI(sum!2^, sum!4)
      d!3 = S!0^ - C!0^
      p!3 = (d!3 * d!3) 
      sum!4 = (sum!3 + p!3)
   sum!3^ = drop_dim(sum!3)     
   !1!2 = (sum!3^ < min_sum!2)
   min_sum!3 = sum!3^
   min_index!3 = i  // Same-level, will lift when hoisted
   min_sum!4 = MUX(!1!2, min_sum!3, min_sum!2)
   min_index!4 = MUX(!1!2, min_index!3, min_index!2)
min_sum!2^ = drop_dim(min_sum!2)
min_index!2^ = drop_dim(min_index!2)   
!2!1 = (min_sum!2^, min_index!2^)     
\end{verbatim}
}

@@

{\small
\begin{verbatim}
min_sum!1 = 10000
min_sum!1^ = raise_dim(min_sum!1, (i:N!0))
min_index!1 = 0
min_index!1^ = raise_dim(min_index!1, (i:N!0))
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0,j:D!0))
for i in range(0, N!0):
  min_sum!2[I] = PHI(min_sum!1^[I], min_sum!4[I]) 
  min_index!2[I] = PHI(min_index!1^[I], min_index!4[I])  
  sum!2 = [0,..,0] 
  sum!2^ = raise_dim(sum!2, (j:D!0))
  d!3[I,J] = S!0^[I,J] - C!0^[I,J]
  p!3[I,J] = (d!3[I,J] * d!3[I,J])
  for j in range(0, D!0):
    sum!3[I,j] = PHI(sum!2^[I,j], sum!4[I,j-1])       
    sum!4[I,j] = (sum!3[I,j] + p!3[I,j])
  sum!3^ = drop_dim(sum!3)     
  !1!2[I] = (sum!3^[I] < min_sum!2[I])
  min_sum!3 = sum!3^
  min_index!3 = [0,1,2,...,N!0-1]
  min_sum!4[I] = MUX(!1!2[I], min_sum!3[I], min_sum!2[I])
   min_index!4[I] = MUX(!1!2[I], min_index!3[I], min_index!2[I])
min_sum!2^ = drop_dim(min_sum!2)
min_index!2^ = drop_dim(min_index!2)   
!2!1 = (min_sum!2^, min_index!2^)
\end{verbatim}
}

@@

for i in range(0, N!0):
  min_index!2[i] = PHI(min_index!1^[i], min_index!4[i-1])  
   min_index!4[i] = MUX(!1!2[i], min_index!3[i], min_index!2[i])

min_sum!2^ = drop_dim(min_sum!2)
min_index!2^ = drop_dim(min_index!2)   
!2!1 = (min_sum!2^, min_index!2^)
\end{verbatim}
}
